\pkg{DNest4}: Diffusive Nested Sampling in \proglang{C++} and \proglang{Python}

### 2016-05-24 paper/ms.tex
Talking about randh

\subsection{Equal weight enforcement}
This value is the parameter $\beta$ described in \citet{dnest4}, and compensates
for imprecision in the spacing of the levels, so that the desired mixture
weights $w_j \propto 1$ are achieved during the second stage of the DNS
algorithm. The value 100 is recommended.

@@

This first chooses a random integer from $[0, 3)$ using the
\code{rand\_int(int)} member function of the \code{DNest4::RNG} class.
This determines which of the three parameters is modified.

@@

>>>>

\subsection{Equal weight enforcement}
This value is the parameter $\beta$ described in \citet{dnest}, and compensates
for imprecision in the spacing of the levels, so that the desired mixture
weights $w_j \propto 1$ are achieved during the second stage of the DNS
algorithm. The value 100 is recommended.

@@

This first chooses a random integer from $[0, 3)$ using the
\code{rand\_int(int)} member function of the \code{DNest4::RNG} class.
This determines which of the three parameters
$(m, b, \sigma)$ is modified.

\subsection{Proposals for single parameters}
The proposal for $m$ involves adding a perturbation to the current value
using the line \code{m += 1E3*rng.randh();}.

A challenge using MCMC for standard Nested Sampling is that the target
distribution is not static --- it gets compressed over time. Similarly, in
the first stage of DNS the target distribution gets compressed (as levels are
added), and in the second stage the target distribution is a mixture of
distributions that have been compressed to varying degrees.

Rather than trying to adapt proposal distributions as a function of level,
it is much simpler to just use heavy-tailed proposals which have some
probability of making a jump of appropriate size. This may seem slightly
wasteful of CPU time, but it saves a lot of human time.
In simple experiments, we have found that heavy-tailed proposals are
about as efficient as slice sampling \citep{slice}, but much easier to
implement. The following procedure generates
$x$ from a heavy-tailed distribution:

\begin{enumerate}
\item Generate $c \sim$ Cauchy$(0, 1)$
\item Generate $n \sim$ Normal$(0, 1)$
\item Set $x := 10^{1.5 - |c|}n$
\end{enumerate}
This generates values with a maximum scale of tens-hundreds, down to
the smallest positive value in double precision, by virtue
of the Cauchy distribution's heavy tails.

For convenience, the \code{RNG} class contains a member function \code{randh()}
to generate values from this distribution.

The factor of \code{1E3} is
included to account for the prior width.

@@

\bibitem[Neal(2003)]{slice}
Neal, R.M., 2003. Slice sampling. Annals of statistics, pp.705-741.
